### 2014-11-12 ms.tex
Starting

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=2.5cm,top=2.5cm,right=2.5cm]{geometry}
\usepackage{parskip}
\usepackage{amsmath}

\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}

\newcommand{\hyperparams}{\boldsymbol{\alpha}}
\newcommand{\xx}{\mathbf{x}}

\title{What is MaxEnt?}
\author{Brendon J. Brewer}

\begin{document}
\maketitle

Relative entropy
\begin{eqnarray}
H(\mathbf{p}; \mathbf{q}) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
\end{eqnarray}

\begin{thebibliography}{}
\end{thebibliography}

\end{document}

### 2014-11-24 ms.tex
Words
language example

@@
 \usepackage{amsmath}
+\usepackage[utf8]{inputenc}
 
@@
 
+\section{Testable Information}
+
+\section{Where does testable information come from?}
+
+Example about hearing ``sí/si'' as an answer to a question,
+and inferring the language (Spanish or French).
+
+The joint prior is:
+
+\begin{eqnarray}
+\begin{array}{|c|c|c|}
+\hline
+	&	S	& \bar{S}\\
+\hline
+H_1 & 0.25  & 0.25\\
+H_2 & 0.05 & 0.45\\
+\hline
+\end{array}
+\end{eqnarray}
+
+The marginal probabilities for $H_1$ and $H_2$ are both 0.5, and the
+marginal probabilities for $S$ and $\bar{S}$ are 0.3 and 0.7 respectively.
+
+\section{MaxEnt and Bayesian Inference}
+
+\section{MaxEnt and Hierarchical Bayesian Models}
+
 \begin{thebibliography}{}

### 2014-11-24 ms.tex
Random writing

@@
 
+\section{A Special Case: Expected Values}\label{sec:expectations}
+Refer to Jaynes here...I don't want to present all the details.
+
 \section{Where does testable information come from?}
@@
 H_1 & 0.25  & 0.25\\
+\hline
 H_2 & 0.05 & 0.45\\
@@
 
-\section{MaxEnt and Bayesian Inference}
+\section{MaxEnt and Bayesian Inference}\label{sec:bayes}
 
 \section{MaxEnt and Hierarchical Bayesian Models}
+Suppose we have a prior distribution $q(\mathbf{x})$ describing a state of
+knowledge about a vector of quantities $\mathbf{x}$. Consider some
+function of the unknowns, such as $f(\mathbf{x}) = \sum_{i=1}^N x_i$.
+If the value of $f$ is known, then our distribution for $\mathbf{x}$ can
+be updated as in Section~\ref{sec:bayes}. If we receive testable information
+about the expected value of $f$, then our distribution for $\mathbf{x}$ can
+be updated as in Section~\ref{sec:expectations}.
+
+In this section we'll look at a different kind of testable information that
+relates to $f$, but is not the expected value. What if we receive testable
+information about the marginal distribution for $f$?
+
+To keep things concrete, suppose all of the unknown parameters are positive,
+and our prior is an improper uniform distribution:
+
+\begin{eqnarray}
+q(\mathbf{x}) \propto
+\left\{
+\begin{array}{lr}
+1, & \forall x_i > 0\\
+0, & \textnormal{otherwise}.
+\end{array}
+\right.
+\end{eqnarray}
 
 \begin{thebibliography}{}
+Jaynes, E. T., 1979, `Where do we Stand on Maximum Entropy?' in The Maximum Entropy Formalism, R. D. Levine and M. Tribus (eds.), M. I. T. Press, Cambridge, MA, p. 15
 \end{thebibliography}

### 2014-11-24 ms.tex
minor words

@@
 knowledge about a vector of quantities $\mathbf{x}$. Consider some
-function of the unknowns, such as $f(\mathbf{x}) = \sum_{i=1}^N x_i$.
-If the value of $f$ is known, then our distribution for $\mathbf{x}$ can
+function of the unknowns, such as $F=f(\mathbf{x}) = \sum_{i=1}^N x_i$.
+If the value of $F$ is known, then our distribution for $\mathbf{x}$ can
 be updated as in Section~\ref{sec:bayes}. If we receive testable information
-about the expected value of $f$, then our distribution for $\mathbf{x}$ can
+about the expected value of $F$, then our distribution for $\mathbf{x}$ can
 be updated as in Section~\ref{sec:expectations}.
@@
 
+For any distribution $p(\mathbf{x})$, the marginal distribution for $F$ is:
+
+\begin{eqnarray}
+p(F) &=& \int \delta\left(F - f(\mathbf{x})\right)p(\mathbf{x}) \, d^n \mathbf{x}
+\end{eqnarray}
+
 \begin{thebibliography}{}

### 2015-06-11 ms.tex
Boldsymbol

--- 2014-11-24 ms.tex
@@
 \newcommand{\hyperparams}{\boldsymbol{\alpha}}
-\newcommand{\xx}{\mathbf{x}}
+\newcommand{\xx}{\boldsymbol{x}}
 
@@
 \begin{eqnarray}
-H(\mathbf{p}; \mathbf{q}) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
+H(\boldsymbol{p}; \boldsymbol{q}) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
 \end{eqnarray}
@@
 \section{MaxEnt and Hierarchical Bayesian Models}
-Suppose we have a prior distribution $q(\mathbf{x})$ describing a state of
-knowledge about a vector of quantities $\mathbf{x}$. Consider some
-function of the unknowns, such as $f(\mathbf{x}) = \sum_{i=1}^N x_i$.
-If the value of $f$ is known, then our distribution for $\mathbf{x}$ can
+Suppose we have a prior distribution $q(\boldsymbol{x})$ describing a state of
+knowledge about a vector of quantities $\boldsymbol{x}$. Consider some
+function of the unknowns, such as $F=f(\boldsymbol{x}) = \sum_{i=1}^N x_i$.
+If the value of $F$ is known, then our distribution for $\boldsymbol{x}$ can
 be updated as in Section~\ref{sec:bayes}. If we receive testable information
-about the expected value of $f$, then our distribution for $\mathbf{x}$ can
+about the expected value of $F$, then our distribution for $\boldsymbol{x}$ can
 be updated as in Section~\ref{sec:expectations}.
@@
 \begin{eqnarray}
-q(\mathbf{x}) \propto
+q(\boldsymbol{x}) \propto
 \left\{
@@
 
+For any distribution $p(\boldsymbol{x})$, the marginal distribution for $F$ is:
+
+\begin{eqnarray}
+p(F) &=& \int \delta\left(F - f(\boldsymbol{x})\right)p(\boldsymbol{x}) \, d^n \boldsymbol{x}
+\end{eqnarray}
+
 \begin{thebibliography}{}

### 2015-06-12 ms.tex
working out stuff

@@
 
-To keep things concrete, suppose all of the unknown parameters are positive,
-and our prior is an improper uniform distribution:
-
+For any distribution $p(\boldsymbol{x})$, the marginal distribution for $F$ is:
 \begin{eqnarray}
-q(\boldsymbol{x}) \propto
-\left\{
-\begin{array}{lr}
-1, & \forall x_i > 0\\
-0, & \textnormal{otherwise}.
-\end{array}
-\right.
+p(F) &=& \int \delta\left(F - f(\boldsymbol{x})\right)p(\boldsymbol{x}) \, d^n \boldsymbol{x}\label{eqn:constraint}
+\end{eqnarray}
+If $p(F)$ is a specified function, this is an infinite number of expected
+value constraints on $p(\xx)$. Therefore the probability distribution
+$p(\xx)$ with maximum entropy with respect to $q(\xx)$ that satisfies the
+constraint~\ref{eqn:constraint} is:
+\begin{eqnarray}
+p(\xx) &=& \frac{q(\xx)}{Z}\exp\left[- \right]
 \end{eqnarray}
 
-For any distribution $p(\boldsymbol{x})$, the marginal distribution for $F$ is:
+%To keep things concrete, suppose all of the unknown parameters are positive,
+%and our prior is an improper uniform distribution:
 
-\begin{eqnarray}
-p(F) &=& \int \delta\left(F - f(\boldsymbol{x})\right)p(\boldsymbol{x}) \, d^n \boldsymbol{x}
-\end{eqnarray}
+%\begin{eqnarray}
+%q(\boldsymbol{x}) \propto
+%\left\{
+%\begin{array}{lr}
+%1, & \forall x_i > 0\\
+%0, & \textnormal{otherwise}.
+%\end{array}
+%\right.
+%\end{eqnarray}
 

### 2015-06-14 ms.tex
back to discrete

@@
 \usepackage{amsmath}
+\usepackage{dsfont}
 \usepackage[utf8]{inputenc}
@@
 \section{MaxEnt and Hierarchical Bayesian Models}
-Suppose we have a prior distribution $q(\boldsymbol{x})$ describing a state of
-knowledge about a vector of quantities $\boldsymbol{x}$. Consider some
-function of the unknowns, such as $F=f(\boldsymbol{x}) = \sum_{i=1}^N x_i$.
-If the value of $F$ is known, then our distribution for $\boldsymbol{x}$ can
+Suppose we have a discrete prior distribution $q(\xx)$. Consider some
+function of the unknown quantity, $f(\xx)$.
+If the value of $F$ is known, then our distribution for $\xx$ can
 be updated as in Section~\ref{sec:bayes}. If we receive testable information
-about the expected value of $F$, then our distribution for $\boldsymbol{x}$ can
+about the expected value of $F$, then our distribution for $\xx$ can
 be updated as in Section~\ref{sec:expectations}.
@@
 In this section we'll look at a different kind of testable information that
-relates to $f$, but is not the expected value. What if we receive testable
-information about the marginal distribution for $f$?
+relates to $F$, but is not the expected value. What if we receive testable
+information about the marginal distribution for $F$?
 
-For any distribution $p(\boldsymbol{x})$, the marginal distribution for $F$ is:
+For any distribution $p(\xx)$, the marginal distribution for $F$ is:
 \begin{eqnarray}
-p(F) &=& \int \delta\left(F - f(\boldsymbol{x})\right)p(\boldsymbol{x}) \, d^n \boldsymbol{x}\label{eqn:constraint}
+p(F) &=& \sum_{\xx}\mathds{1}\left(f(\xx) = F\right)p(\xx)\label{eqn:constraint}
 \end{eqnarray}

### 2015-06-14 ms.tex
Working out the maxent solution

@@
 \begin{eqnarray}
-p(F) &=& \sum_{\xx}\mathds{1}\left(f(\xx) = F\right)p(\xx)\label{eqn:constraint}
+p(F) &=& \sum_{\xx}\mathds{1}\left[f(\xx) = F\right]p(\xx)\label{eqn:constraint}
 \end{eqnarray}
-If $p(F)$ is a specified function, this is an infinite number of expected
-value constraints on $p(\xx)$. Therefore the probability distribution
+If $p(F)$ is a specified function, this is a large number of expected
+value constraints on $p(\xx)$, one for each element of the hypothesis space
+of possible $F$ values.
+
+Therefore the probability distribution
 $p(\xx)$ with maximum entropy with respect to $q(\xx)$ that satisfies the
@@
 \begin{eqnarray}
-p(\xx) &=& \frac{q(\xx)}{Z}\exp\left[- \right]
+p(\xx) &=& \frac{q(\xx)}{Z}\exp\left\{-\sum_F \lambda_F \mathds{1}
+\left[f(\xx) = F\right]  \right\}
 \end{eqnarray}

### 2015-06-14 ms.tex
Some references

@@
 
-%To keep things concrete, suppose all of the unknown parameters are positive,
-%and our prior is an improper uniform distribution:
+\begin{thebibliography}{}
+\bibitem[Caticha(2008)]{2008arXiv0808.0012C} Caticha, A.\ 2008.\ Lectures 
+on Probability, Entropy, and Statistical Physics.\ ArXiv e-prints 
+arXiv:0808.0012.
 
-%\begin{eqnarray}
-%q(\boldsymbol{x}) \propto
-%\left\{
-%\begin{array}{lr}
-%1, & \forall x_i > 0\\
-%0, & \textnormal{otherwise}.
-%\end{array}
-%\right.
-%\end{eqnarray}
+\bibitem[Caticha and Giffin(2006)]{2006AIPC..872...31C} Caticha, A., 
+Giffin, A.\ 2006.\ Updating Probabilities.\ Bayesian Inference and Maximum 
+Entropy Methods In Science and Engineering 872, 31-42.
 
-\begin{thebibliography}{}
-Jaynes, E. T., 1979, `Where do we Stand on Maximum Entropy?' in The Maximum Entropy Formalism, R. D. Levine and M. Tribus (eds.), M. I. T. Press, Cambridge, MA, p. 15
+\bibitem[Giffin and Caticha(2007)]{2007AIPC..954...74G} Giffin, A., 
+Caticha, A.\ 2007.\ Updating Probabilities with Data and Moments.\ Bayesian 
+Inference and Maximum Entropy Methods in Science and Engineering 954, 
+74-84.
+
+\bibitem[Jaynes(1979)]{stand_on_entropy} Jaynes, E.
+T., 1979, ``Where do we Stand on Maximum Entropy?'' in The Maximum Entropy Formalism, R.
+D.
+Levine and M.
+Tribus (eds.), M.
+I.
+T.
+Press, Cambridge, MA, p.
+15
 \end{thebibliography}

### 2015-06-14 ms.tex
minor edits

@@
 function of the unknown quantity, $f(\xx)$.
-If the value of $F$ is known, then our distribution for $\xx$ can
-be updated as in Section~\ref{sec:bayes}. If we receive testable information
+If the value of $f(\xx)$ is known, then our distribution for $\xx$ can
+be updated from $q$ to $p$ as in Section~\ref{sec:bayes}.
+If we receive testable information
 about the expected value of $F$, then our distribution for $\xx$ can
@@
 relates to $F$, but is not the expected value. What if we receive testable
-information about the marginal distribution for $F$?
-
+information that asserts the marginal distribution for $F$?
 For any distribution $p(\xx)$, the marginal distribution for $F$ is:
@@
 value constraints on $p(\xx)$, one for each element of the hypothesis space
-of possible $F$ values.
+of possible $F$ values. Clearly, the specified marginal $p(F)$ cannot assign
+non-zero probability to any possible $F$ values that have zero probability
+under $q(\xx)$.
 
-Therefore the probability distribution
+Since Equation~\ref{eqn:constraint} is really just a set of expectations,
+the probability distribution
 $p(\xx)$ with maximum entropy with respect to $q(\xx)$ that satisfies the

### 2015-06-15 ms.tex
Intro words, Jaynes 2003 reference

@@
 \maketitle
+
+The principle of maximum entropy (MaxEnt) is an idea in probability theory
+that is usually associated with \citet{jaynes}. The principle may be used
+to {\it assign} or {\it update} a
+subjective\footnote{in the sense that the probability distribution is a model
+of the state of uncertainty of an idealised rational agent.}
+probability distribution when you obtain a certain kind of information
+called {\it testable information}.
 
@@
 15
+
+\bibitem[Jaynes(2003)]{jaynes} Jaynes, E. T., 2003, ``Probability Theory:
+The Logic of Science'', ed. G.~Larry~Bretthorst, Cambridge University Press
+
 \end{thebibliography}

### 2015-06-15 ms.tex
More refs and words

--- 2015-06-14 ms.tex
@@
 
-\title{What is MaxEnt?}
+\title{MaxEnt: What is it good for?}
 \author{Brendon J. Brewer}
@@
 \maketitle
+
+The principle of maximum entropy (MaxEnt) is an idea in probability theory
+that is usually associated with \citet{jaynes}. The principle may be used
+to {\it assign} or {\it update} a
+subjective\footnote{in the sense that the probability distribution is a model
+of the state of uncertainty of an idealised rational agent, rather than
+a {\it frequency distribution} such as a histogram of people's heights.}
+probability distribution when you obtain a certain kind of information
+called {\it testable information}. The principle is very intuitively compelling
+and there are some axiomatic arguments in its favour
+\citep[e.g.][]{2010arXiv1008.4831K}. However, MaxEnt has also been widely
+misapplied (even by some of its staunchest defenders), misunderstood,
+and poorly defended (even by Jaynes himself).
 
@@
 
-\section{Testable Information}
+\section{What is testable information?}
 
-\section{A Special Case: Expected Values}\label{sec:expectations}
+\section{A special case: expected values}\label{sec:expectations}
 Refer to Jaynes here...I don't want to present all the details.
 
-\section{Where does testable information come from?}
+\section{Where is testable information in the real world?}
 
@@
 
-\section{MaxEnt and Bayesian Inference}\label{sec:bayes}
+\section{MaxEnt and Bayesian inference}\label{sec:bayes}
 
-\section{MaxEnt and Hierarchical Bayesian Models}
+\section{MaxEnt and ``Hierarchical Bayesian'' models}
 Suppose we have a discrete prior distribution $q(\xx)$. Consider some
@@
 15
+
+\bibitem[Jaynes(2003)]{jaynes} Jaynes, E. T., 2003, ``Probability Theory:
+The Logic of Science'', ed. G.~Larry~Bretthorst, Cambridge University Press
+
+\bibitem[Knuth and Skilling(2010)]{2010arXiv1008.4831K} Knuth, K.~H., 
+Skilling, J.\ 2010.\ Foundations of Inference.\
+Axioms 1.1 (2012): 38-73.\
+ArXiv e-prints arXiv:1008.4831. 
 \end{thebibliography}

### 2015-06-15 ms.tex
People use it to justify priors

@@
 misapplied (even by some of its staunchest defenders), misunderstood,
-and poorly defended (even by Jaynes himself).
+and poorly defended (at times, even by Jaynes himself).
+Consequently, most modern Bayesians pay little attention to the principle,
+although there is a tendency among physicists to invoke it as a justification
+for a prior distribution (be it uniform, exponential, gaussian, or whatever).
 

### 2015-06-16 ms.tex
hypothesis space
Acknowledgements

@@
 
+We start with a {\it hypothesis space} of mutually exclusive and
+exhaustive propositions $A_1$, $A_2$, ..., $A_N$. One and only one of these
+propositions is true, but we don't know which.
+
 Relative entropy
@@
 \section{What is testable information?}
+
+\section{A special case: updating given propositions}
 
@@
 
+\section*{Acknowledgements}
+It is a pleasure to thank
+Ariel Caticha (Albany),
+John Skilling (MaxEnt Data Consultants),
+Carlos Rodriguez (),
+Stephen Gull (),
+Kevin Knuth (Albany),
+Iain Murray (Edinburgh),
+Anna Pancoast (UCSB),
+Geraint Lewis (Sydney),
+David Hogg (NYU),
+Tom Loredo (Cornell),
+Daniela Huppenkothen (NYU),
+Peter Tuthill (Sydney),
+
 \begin{thebibliography}{}

### 2015-06-16 ms.tex
Probability distribution properties

@@
 exhaustive propositions $A_1$, $A_2$, ..., $A_N$. One and only one of these
-propositions is true, but we don't know which.
+propositions is true, but we don't know which. We model states of
+uncertainty by probability distributions over the hypothesis space,
+such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
+Of course all of the $p_i$ must be non-negative and their sum must be 1.
+From this probability distribution, various probabilities can be derived
+using the sum and product rules. For example, the probability of
+$A_4$ {\bf or} $A_5$ is $p_4 + p_5$, and the probability of $A_5$ given
+$A_5$ {\bf or} $A_6$ is $p_5/(p_5 + p_6)$. The rules of probability must
+be obeyed if the rules for combining are to remain consistent
+with the symmetries of logical {\bf and} and {\bf or} \citep{knuth_skilling}.
 

### 2015-06-16 ms.tex
Fixed citation

@@
 be obeyed if the rules for combining are to remain consistent
-with the symmetries of logical {\bf and} and {\bf or} \citep{knuth_skilling}.
+with the symmetries of logical {\bf and} and {\bf or}
+\citep{2010arXiv1008.4831K}.
 

### 2015-06-16 ms.tex
Article purpose
bracket fixes

@@
 for a prior distribution (be it uniform, exponential, gaussian, or whatever).
+The purpose of this article is to explore the principle from the point of
+view of a Bayesian practitioner, discuss some of the properties that
+make MaxEnt compelling, and propose some ideas about how it could be used in
+practice.
 
 We start with a {\it hypothesis space} of mutually exclusive and
-exhaustive propositions $A_1$, $A_2$, ..., $A_N$. One and only one of these
+exhaustive propositions $\{A_1, A_2, ..., A_N\}$. One and only one of these
 propositions is true, but we don't know which. We model states of
@@
 using the sum and product rules. For example, the probability of
-$A_4$ {\bf or} $A_5$ is $p_4 + p_5$, and the probability of $A_5$ given
-$A_5$ {\bf or} $A_6$ is $p_5/(p_5 + p_6)$. The rules of probability must
+($A_4$ {\bf or} $A_5$) is $p_4 + p_5$, and the probability of $A_5$ given
+($A_5$ {\bf or} $A_6$) is $p_5/(p_5 + p_6)$. The rules of probability must
 be obeyed if the rules for combining are to remain consistent

### 2015-06-16 ms.tex
Mention I
More writing

@@
 We start with a {\it hypothesis space} of mutually exclusive and
-exhaustive propositions $\{A_1, A_2, ..., A_N\}$. One and only one of these
+exhaustive propositions $\{A_1, A_2, ..., A_N\}$ which we will sometimes
+describe as possible values $\{x_1, x_2, ..., x_N\}$ of an unknown variable $x$.
+On the basis of background
+information $I$ (hereafter suppressed), we know that one and only one of these
 propositions is true, but we don't know which. We model states of
@@
 \section{A special case: expected values}\label{sec:expectations}
-Refer to Jaynes here...I don't want to present all the details.
+The most common kind of testable information analysed using MaxEnt is
+expected values. Updating from a prior $\boldsymbol{q}$ to a posterior
+$\boldsymbol{p}$ given an expected value constraint:
+
+\begin{eqnarray}
+\left<f(x)\right>_{\boldsymbol{p}} = \sum_{i=1}^N p_i f(x_i) = F.
+\end{eqnarray}
+
+The resulting posterior distribution given by MaxEnt is:
+
+\begin{eqnarray}
+p(x) &=& \frac{1}{Z}q(x)\exp\left[-\lambda f(x)\right] 
+\end{eqnarray}
 

### 2015-06-17 plots.py
Plots

@@ -1,0 +1,21 @@
+from pylab import *
+
+seed(123)
+rc("font", size=16, family="serif", serif="Computer Sans")
+rc("text", usetex=True)
+
+x = 1 + arange(0, 10)
+
+# Make a prior
+p = exp(0.5*randn(x.size))
+p /= p.sum()
+
+bar(x-0.5*0.35, p, width=0.35, alpha=0.3)
+xlabel("$x$", fontsize=20)
+ylabel("Probability")
+xlim([0.5, 10.5])
+gca().set_xticks(x)
+title("A Probability Distribution")
+savefig("distribution.pdf", bbox_inches="tight")
+show()
+

### 2015-06-17 ms.tex
Plots
gotta think about notation

@@
 
+\section{Probability}
 We start with a {\it hypothesis space} of mutually exclusive and
-exhaustive propositions $\{A_1, A_2, ..., A_N\}$ which we will sometimes
-describe as possible values $\{x_1, x_2, ..., x_N\}$ of an unknown variable $x$.
+exhaustive propositions $\{A_1, A_2, ..., A_N\}$ which we will usually
+think of as possible values of an unknown quantity $x$.
 On the basis of background
 information $I$ (hereafter suppressed), we know that one and only one of these
-propositions is true, but we don't know which. We model states of
+propositions is true (i.e. the true value of $x$ is in our set),
+but we don't know which. We model states of
 uncertainty by probability distributions over the hypothesis space,
 such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
+The standard loose Bayesian notation would write this distribution simply
+as $p(x)$.
+
 Of course all of the $p_i$ must be non-negative and their sum must be 1.
@@
 ($A_4$ {\bf or} $A_5$) is $p_4 + p_5$, and the probability of $A_5$ given
-($A_5$ {\bf or} $A_6$) is $p_5/(p_5 + p_6)$. The rules of probability must
+($A_5$ {\bf or} $A_8$) is $p_5/(p_5 + p_8)$. The rules of probability must
 be obeyed if the rules for combining are to remain consistent
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{distribution.pdf}
+\caption{\label{fig:distribution}}
+\end{center}
+\end{figure}
+
 Relative entropy
 \begin{eqnarray}
-H(\boldsymbol{p}; \boldsymbol{q}) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
+H(p; q) &=& -\sum_i p_i \log\left(\frac{p_i}{q_i}\right) 
 \end{eqnarray}

### 2015-06-18 ms.tex
Words around entropy formula
Testable information that's equivalent to conditioning

@@
 
-Relative entropy
+The relative entropy of distribution $p$ from distribution $q$ is:
 \begin{eqnarray}
@@
 \end{eqnarray}
+and we are to choose the distribution $p$ to maximise $H$ subject to the
+constraints of normalisation and any other constraints.
 
@@
 \section{A special case: updating given propositions}
+Consider the following testable information:
+
+\begin{eqnarray}
+P(D) = 1
+\end{eqnarray}
+where $D$ is a proposition about the value of $x$. For example, consider
+updating from the prior $q(x)$ shown in Figure~\ref{fig:distribution}, to
+a posterior $p(x)$, using the testable information
+\begin{eqnarray}
+P(3 \leq x \leq 5) = 1.
+\end{eqnarray}
 

### 2015-06-18 ms.tex
Abstract and intro words

@@
-\documentclass[letterpaper, 11pt]{article}
+\documentclass[a4paper, 11pt]{article}
 \usepackage{graphicx}
@@
 
+\abstract{I discuss the principle of maximum (relative) entropy as a tool
+for updating probability distributions. This principle is intuitively
+compelling, as I will show through examples. However, it has been neglected
+by most modern practitioners of Bayesian inference. I will argue that there
+are two main reasons for this: i) some questionable applications
+and discussions of the principle have appeared in the literature, and
+ii) the situation which the principle seems designed to handle never seems
+to arise in practical applications.}
+
+\section{Introduction}
 The principle of maximum entropy (MaxEnt) is an idea in probability theory
-that is usually associated with \citet{jaynes}. The principle may be used
+that is usually associated with \citet{jaynes}, although it has appeared in
+various guises in the work of others \citep[e.g.][]{gibbs, boltzmann, shannon}.
+
+The principle may be used
 to {\it assign} or {\it update} a
@@
 probability distribution when you obtain a certain kind of information
-called {\it testable information}. The principle is very intuitively compelling
+called {\it testable information}. In this article I will focus on the
+updating application, as the assigning application can be viewed as a special
+case where the prior distribution happened to be
+uniform\footnote{A uniform probability distribution, either over a discrete
+hypothesis space, or a continuous one with respect to a continuous, may be
+justified by a symmetry argument or simply asserted as in the
+``subjective Bayesian'' approach.}.
+
+The principle is very intuitively compelling
 and there are some axiomatic arguments in its favour

### 2015-06-18 ms.tex
Giffin!

@@
 Ariel Caticha (Albany),
+Adom Giffin (Clarkson)
 John Skilling (MaxEnt Data Consultants),
-Carlos Rodriguez (),
-Stephen Gull (),
+Carlos Rodriguez (Albany),
+Stephen Gull (Cambridge),
 Kevin Knuth (Albany),

### 2015-06-19 plots.py
Posterior plot

@@ -7,15 +7,30 @@ rc("text", usetex=True)
 x = 1 + arange(0, 10)
 
 # Make a prior
-p = exp(0.5*randn(x.size))
+q = exp(0.5*randn(x.size))
+q /= q.sum()
+
+bar(x-0.5*0.35, q, width=0.35, alpha=0.3)
+xlabel("$x$", fontsize=20)
+ylabel("Probability, $q(x)$")
+xlim([0.5, 10.5])
+gca().set_xticks(x)
+title("Prior Distribution")
+savefig("distribution.pdf", bbox_inches="tight")
+show()
+
+
+# Make a posterior
+p = q.copy()
+p[logical_or(x < 3, x > 5)] = 0.
 p /= p.sum()
 
 bar(x-0.5*0.35, p, width=0.35, alpha=0.3)
 xlabel("$x$", fontsize=20)
-ylabel("Probability")
+ylabel("Probability, $p(x)$")
 xlim([0.5, 10.5])
 gca().set_xticks(x)
-title("A Probability Distribution")
-savefig("distribution.pdf", bbox_inches="tight")
+title("Posterior Distribution")
+savefig("distribution2.pdf", bbox_inches="tight")
 show()
 

### 2015-06-19 ms.tex
sentence
New figure, tweaks

@@
 uniform\footnote{A uniform probability distribution, either over a discrete
-hypothesis space, or a continuous one with respect to a continuous, may be
-justified by a symmetry argument or simply asserted as in the
-``subjective Bayesian'' approach.}.
+hypothesis space, or a continuous one with respect to a specific choice of
+parameterisation, may be justified by a symmetry argument, or simply asserted
+as in the ``subjective Bayesian'' approach.}.
 
@@
 We start with a {\it hypothesis space} of mutually exclusive and
-exhaustive propositions $\{A_1, A_2, ..., A_N\}$ which we will usually
-think of as possible values of an unknown quantity $x$.
+exhaustive propositions $A_1$, $A_2$, ..., $A_N$ which we will usually
+think of as possible values of an unknown quantity $x$. For example,
+$A_1 \equiv $``$x=1$'', $A_2 \equiv $``$x=2$'', and so on.
 On the basis of background
@@
 \end{eqnarray}
+
+Clearly, the distribution $q(x)$ doesn't satisfy this constraint, so we
+need to update to a new distribution $p(x)$ using MaxEnt.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{distribution2.pdf}
+\caption{\label{fig:distribution2}}
+\end{center}
+\end{figure}
 

### 2015-06-19 ms.tex
Abstract edits

@@
 compelling, as I will show through examples. However, it has been neglected
-by most modern practitioners of Bayesian inference. I will argue that there
+by most modern practitioners of Bayesian inference. There
 are two main reasons for this: i) some questionable applications
@@
 ii) the situation which the principle seems designed to handle never seems
-to arise in practical applications.}
+to actually arise in practical applications. I will attempt to define the
+situations in which MaxEnt could be practically useful.}
 

### 2015-06-19 ms.tex
john w

@@
 Peter Tuthill (Sydney),
+and John Wilcox (Auckland)
+for valuable discussions.
 

### 2015-06-19 ms.tex
gibbs
Some edits

@@
 information $I$ (hereafter suppressed), we know that one and only one of these
-propositions is true (i.e. the true value of $x$ is in our set),
+propositions is true (i.e. the true value of $x$ is in our hypothesis space),
 but we don't know which. We model states of
@@
 such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
-The standard loose Bayesian notation would write this distribution simply
+In the standard loose Bayesian notation we write this distribution simply
 as $p(x)$.
 
-Of course all of the $p_i$ must be non-negative and their sum must be 1.
+Of course, $p(x)$ must be non-negative and sum to 1.
 From this probability distribution, various probabilities can be derived
@@
 \end{eqnarray}
+Intuitively, $H$ measures how close the probability distribution $p$ is
+to the distribution $q$. The maximum possible value of $H$ is zero, if
+and only if $p$ happens to be the same as $q$.
+However, it is not symmetric and does not satisfy
+other properties of a distance.
 and we are to choose the distribution $p$ to maximise $H$ subject to the
@@
 
+\bibitem[Gibbs(1914)]{gibbs} Gibbs, J.~W.~Elementary Principles in
+Statistical Mechanics: Developed with Special Reference to the Rational
+Foundations of Thermodynamics. Yale University Press, 1914.
+
 \bibitem[Giffin and Caticha(2007)]{2007AIPC..954...74G} Giffin, A., 

### 2015-06-19 ms.tex
Some writing and reordering

@@
 
+Throughout this article I will present, but not derive or prove, MaxEnt
+results for certain types of testable information.
+
 \section{Probability}
@@
 \section{What is testable information?}
+{\it Testable information} refers to information given in the form of
+{\it a constraint that our probability distribution should satisfy}. This is
+different from the kind of information we normally use in Bayesian inference,
+which is the truth of a proposition. An example of testable information
+might be $P(x > 7) = 0.4$. That is, our probability distribution should have
+the property that there's a 40\% probability of $x$ being greater than 7.
+If our current (prior) probability distribution $q$ already has this property,
+then we needn't do anything. However, if $q$ does not satisfy this property,
+we use MaxEnt to choose a new distribution, the posterior $p$.
+
+The posterior $p$ will satisfy the constraint given in the testable information,
+and will be as close to $q$ as possible while doing so.
+
+\section{Special case 1: expected values}\label{sec:expectations}
+The most common kind of testable information analysed using MaxEnt is
+expected values. Updating from a prior $\boldsymbol{q}$ to a posterior
+$\boldsymbol{p}$ given an expected value constraint:
+
+\begin{eqnarray}
+\left<f(x)\right>_{\boldsymbol{p}} = \sum_{i=1}^N p_i f(x_i) = F.
+\end{eqnarray}
+
+The resulting posterior distribution given by MaxEnt is:
+
+\begin{eqnarray}
+p(x) &=& \frac{1}{Z}q(x)\exp\left[-\lambda f(x)\right] 
+\end{eqnarray}
 
@@
 
-\section{A special case: expected values}\label{sec:expectations}
-The most common kind of testable information analysed using MaxEnt is
-expected values. Updating from a prior $\boldsymbol{q}$ to a posterior
-$\boldsymbol{p}$ given an expected value constraint:
+\section{MaxEnt with constraints on conditionals: the ``entropic prior''}
 
-\begin{eqnarray}
-\left<f(x)\right>_{\boldsymbol{p}} = \sum_{i=1}^N p_i f(x_i) = F.
-\end{eqnarray}
-
-The resulting posterior distribution given by MaxEnt is:
-
-\begin{eqnarray}
-p(x) &=& \frac{1}{Z}q(x)\exp\left[-\lambda f(x)\right] 
-\end{eqnarray}
-
-\section{Where is testable information in the real world?}
-
-Example about hearing ``sí/si'' as an answer to a question,
-and inferring the language (Spanish or French).
-
-The joint prior is:
-
-\begin{eqnarray}
-\begin{array}{|c|c|c|}
-\hline
-	&	S	& \bar{S}\\
-\hline
-H_1 & 0.25  & 0.25\\
-\hline
-H_2 & 0.05 & 0.45\\
-\hline
-\end{array}
-\end{eqnarray}
-
-The marginal probabilities for $H_1$ and $H_2$ are both 0.5, and the
-marginal probabilities for $S$ and $\bar{S}$ are 0.3 and 0.7 respectively.
-
-\section{MaxEnt and Bayesian inference}\label{sec:bayes}
-
-\section{MaxEnt and ``Hierarchical Bayesian'' models}
+\section{MaxEnt with constraints on marginals: ``hierarchical Bayes''}
 Suppose we have a discrete prior distribution $q(\xx)$. Consider some
@@
 \end{eqnarray}
+
+\section{Where is testable information in the real world?}
+
+Example about hearing ``sí/si'' as an answer to a question,
+and inferring the language (Spanish or French).
+
+The joint prior is:
+
+\begin{eqnarray}
+\begin{array}{|c|c|c|}
+\hline
+	&	S	& \bar{S}\\
+\hline
+H_1 & 0.25  & 0.25\\
+\hline
+H_2 & 0.05 & 0.45\\
+\hline
+\end{array}
+\end{eqnarray}
+
+The marginal probabilities for $H_1$ and $H_2$ are both 0.5, and the
+marginal probabilities for $S$ and $\bar{S}$ are 0.3 and 0.7 respectively.
 

### 2015-06-19 ms.tex
constraint rule

@@
 The most common kind of testable information analysed using MaxEnt is
-expected values. Updating from a prior $\boldsymbol{q}$ to a posterior
+expected values.
+
+ Updating from a prior $\boldsymbol{q}$ to a posterior
 $\boldsymbol{p}$ given an expected value constraint:
@@
 \end{eqnarray}
+
+\subsection{The ``constraint rule'' controversy}
+Is it valid to use an experimental average (literally the arithmetic mean of
+some data) to set the expected value of a probability distribution? The
+assumption that this is okay has been termed {\it the constraint rule}.
+
+In many presentations of MaxEnt, it is assumed that this is not a problem
+({\bf cite people}). Other authors have noticed that it's possible to
+condition on the observed arithmetic mean, as one would do in a standard
+Bayesian analysis of that information, and that this can lead to a different
+answer from the constraint rule.
 

### 2015-06-19 ms.tex
New section and some more words

@@
 Throughout this article I will present, but not derive or prove, MaxEnt
-results for certain types of testable information.
+results for certain types of testable information. Some of these are well
+known (e.g. the expected value constraints discussed in
+Section~\ref{sec:expected_values}) while others are less so.
 
@@
 
+This has led to the widespread (and in my view, incorrect) belief that
+MaxEnt and Bayesian inference are ``incompatible'', and the
+
 \section{A special case: updating given propositions}
@@
 \end{figure}
+
+\subsection{Skilling's criticism}
+Skilling thinks this is ``deriving Bayes again, when it's already there
+as the product rule''. I consider it more as a demonstration of which
+particular constraints are epistemically equivalent to learning the
+truth of a propositions. It turns out to be the rather obvious constraint
+that the probability we should assign to a proposition we know to be true
+is 1.
+
+I also think this viewpoint clarifies thinking about the ``probability
+distribution for the data'' (interpretation of sampling distributions etc).
 

### 2015-06-20 ms.tex
Niven

@@
 
+{\bf Mention Niven and ``combinatorics'' -- it's just the sum rule then. not
+a new principle}.
+
 \section{A special case: updating given propositions}
@@
 David Hogg (NYU),
+Robert Niven (UNSW),
 Tom Loredo (Cornell),

### 2015-06-21 ms.tex
Brandeis reminder
special cases of canonical

@@
 known (e.g. the expected value constraints discussed in
-Section~\ref{sec:expected_values}) while others are less so.
+Section~\ref{sec:expected_values}, which lead to ``canonical'' probability
+distributions which may be familiar from statistical mechanics) while others
+are less so. Where possible I will present other results as special cases of
+the canonical distribution.
 
@@
 MaxEnt and Bayesian inference are ``incompatible'', and the
+
+{\bf Brandeis dice problem...MaxEnt solution vs. ``the'' Bayesian solution}
 

### 2015-06-21 ms.tex
notation

@@
 The most common kind of testable information analysed using MaxEnt is
-expected values.
-
- Updating from a prior $\boldsymbol{q}$ to a posterior
-$\boldsymbol{p}$ given an expected value constraint:
-
+expected values. An expected value is a property of a probability distribution,
+and we can imagine updating from a prior $q$ to a posterior
+$p$ when we receive information that specifies an expected value.
+For example, suppose we apply the constraint (the testable information)
+that the expected value of $f(x)$ should equal some known value $F$. That is:
 \begin{eqnarray}
-\left<f(x)\right>_{\boldsymbol{p}} = \sum_{i=1}^N p_i f(x_i) = F.
+\left<f(x)\right>_p = \sum_x p(x)f(x) = F.
 \end{eqnarray}

### 2015-06-21 ms.tex
few words in expectation section

@@
 \begin{eqnarray}
-\left<f(x)\right>_p = \sum_x p(x)f(x) = F.
+\left<f(x)\right>_p = \sum_x p(x)f(x) = F.\label{eq:expected_value}
 \end{eqnarray}
@@
 The resulting posterior distribution given by MaxEnt is:
-
 \begin{eqnarray}
@@
 \end{eqnarray}
+That is, the posterior is proportional to the prior multiplied by a
+``canonical'' factor. The value of $\lambda$ must be chosen so that
+the constraint (Equation~\ref{eq:expected_value}) is satisfied. $Z$ is the
+normalisation constant and implicitly depends on $\lambda$.
+
+As an example, let's update the prior from Figure~\ref{fig:distribution}
+using the testable information $\left<(x - 5)^2\right>_p = 1$.
 

### 2015-06-26 ms.tex
Caption
Relate 'updating given propositions' to expected values

@@
 \includegraphics[scale=0.5]{distribution.pdf}
-\caption{\label{fig:distribution}}
+\caption{A prior distribution $q(x)$, which we will use
+update to a posterior $p(x)$ given different kinds of testable information.
+\label{fig:distribution}}
 \end{center}
@@
 \begin{eqnarray}
-P(3 \leq x \leq 5) = 1.
+P(3 \leq x \leq 5) = 1.\label{eq:prob_one}
 \end{eqnarray}
-
-Clearly, the distribution $q(x)$ doesn't satisfy this constraint, so we
-need to update to a new distribution $p(x)$ using MaxEnt.
+Clearly, the distribution $q(x)$ doesn't satisfy this constraint. According
+to $q(x)$ the probability that $x$ is 3, 4, or 5 is 0.225, not 1.
+Therefore, we
+need to update to a new distribution $p(x)$ using MaxEnt. It may not be
+immediately obvious, but Equation~\ref{eq:prob_one} can be viewed as
+a constraint on an expected value:
+\begin{eqnarray}
+\left<
+\mathds{1}\left(3 \leq x \leq 5\right)
+\right>_p = 1.
+\end{eqnarray}
+where $\mathds{1}()$ is an indicator function which returns 1 where the
+argument is true and 0 where it is false. This allows us to use the
+result for expected value constraints, given in
+Section~\ref{sec:expectations}.
 

### 2015-06-26 plots.py

@@ -10,6 +10,9 @@ x = 1 + arange(0, 10)
 q = exp(0.5*randn(x.size))
 q /= q.sum()
 
+# Probability of x \in {3, 4, 5} according to distribution q
+print(sum(q[logical_and(x >= 3, x <= 5)]))
+
 bar(x-0.5*0.35, q, width=0.35, alpha=0.3)
 xlabel("$x$", fontsize=20)
 ylabel("Probability, $q(x)$")

### 2015-06-26 plots.py
Another posterior

@@ -11,7 +11,7 @@ q = exp(0.5*randn(x.size))
 q /= q.sum()
 
 # Probability of x \in {3, 4, 5} according to distribution q
-print(sum(q[logical_and(x >= 3, x <= 5)]))
+#print(sum(q[logical_and(x >= 3, x <= 5)]))
 
 bar(x-0.5*0.35, q, width=0.35, alpha=0.3)
 xlabel("$x$", fontsize=20)
@@ -35,5 +35,22 @@ xlim([0.5, 10.5])
 gca().set_xticks(x)
 title("Posterior Distribution")
 savefig("distribution2.pdf", bbox_inches="tight")
+show()
+
+# Another posterior
+lamb = 0.5163846 # The lagrange multiplier
+p = q.copy()
+p *= exp(-lamb*(x - 5.)**2)
+p /= p.sum()
+e = (p*(x - 5.)**2).sum()
+# print(e)
+
+bar(x-0.5*0.35, p, width=0.35, alpha=0.3)
+xlabel("$x$", fontsize=20)
+ylabel("Probability, $p(x)$")
+xlim([0.5, 10.5])
+gca().set_xticks(x)
+title("Posterior Distribution")
+savefig("distribution3.pdf", bbox_inches="tight")
 show()
 

### 2015-06-26 ms.tex
New figure
Uffink citation

@@
 As an example, let's update the prior from Figure~\ref{fig:distribution}
-using the testable information $\left<(x - 5)^2\right>_p = 1$.
+using the testable information $\left<(x - 5)^2\right>_p = 1$. The appropriate
+value of the lagrange multiplier is $\lambda=0.5163846$, and the posterior is
+shown in Figure~\ref{fig:distribution3}.
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{distribution3.pdf}
+\caption{\label{fig:distribution3}}
+\end{center}
+\end{figure}
 
@@
 some data) to set the expected value of a probability distribution? The
-assumption that this is okay has been termed {\it the constraint rule}.
+assumption that this is okay has been termed {\it the constraint rule}
+\citep{uffink}.
 
@@
 ArXiv e-prints arXiv:1008.4831.
+
+\bibitem[Uffink(1996)]{uffink} Uffink,~J.
+``The constraint rule of the maximum entropy principle.'' Studies in History and Philosophy of Science Part B: Studies in History and Philosophy of Modern Physics 27.1 (1996): 47-79.
 \end{thebibliography}

### 2015-06-28 ms.tex
Some edits

@@
 some data) to set the expected value of a probability distribution? The
-assumption that this is okay has been termed {\it the constraint rule}
-\citep{uffink}.
+assumption that this is okay has been termed {\it the constraint rule}, which
+has been discussed in depth by \citet{uffink}.
 
-In many presentations of MaxEnt, it is assumed that this is not a problem
-({\bf cite people}). Other authors have noticed that it's possible to
+In many presentations of MaxEnt, it is assumed that this is not a problem.
+For example, \citet{jaynes} often motivated MaxEnt using an example of a
+non-standard six-sided die, and we are asked to assign a probability
+distribution for the result of the next toss, using the information that the
+historical average of the tosses is 4.5 instead of the 3.5 one would
+usually expect.
+
+Other authors have noticed that it's possible to
 condition on the observed arithmetic mean, as one would do in a standard

### 2015-06-29 ms.tex
Two new references

@@
 and there are some axiomatic arguments in its favour
-\citep[e.g.][]{2010arXiv1008.4831K}. However, MaxEnt has also been widely
+\citep[e.g.][]{shore_johnson, 2006AIPC..872...31C, 2010arXiv1008.4831K}
+and counterexamples to alternatives \citep[e.g.][]{presse}.
+However, MaxEnt has also been widely
 misapplied (even by some of its staunchest defenders), misunderstood,
@@
 
+\bibitem[Pressé et al(2013)]{presse}
+Pressé, S., et al. ``Nonadditive entropies yield probability distributions with biases not warranted by the data.'' Physical review letters 111.18 (2013): 180604.
+
+\bibitem[Shore and Johnson(1980)]{shore_johnson}
+Shore, J.E., and Johnson, R.. ``Axiomatic derivation of the principle of maximum entropy and the principle of minimum cross-entropy.'' Information Theory, IEEE Transactions on 26.1 (1980): 26-37.
+
 \bibitem[Uffink(1996)]{uffink} Uffink,~J.

### 2015-07-01 plots.py
prior and posterior together

@@ -28,12 +28,20 @@ p = q.copy()
 p[logical_or(x < 3, x > 5)] = 0.
 p /= p.sum()
 
+figure(figsize=(8, 10))
+subplot(2,1,1)
+bar(x-0.5*0.35, q, width=0.35, alpha=0.3)
+xlim([0.5, 10.5])
+ylim([0., 1.05*max(hstack([q, p]))])
+gca().set_xticks(x)
+ylabel("Probability, $q(x)$")
+subplot(2,1,2)
 bar(x-0.5*0.35, p, width=0.35, alpha=0.3)
 xlabel("$x$", fontsize=20)
 ylabel("Probability, $p(x)$")
 xlim([0.5, 10.5])
+ylim([0., 1.05*max(hstack([q, p]))])
 gca().set_xticks(x)
-title("Posterior Distribution")
 savefig("distribution2.pdf", bbox_inches="tight")
 show()
 

### 2015-07-01 plots.py
Double plot for another figure

@@ -53,12 +53,20 @@ p /= p.sum()
 e = (p*(x - 5.)**2).sum()
 # print(e)
 
+figure(figsize=(8, 10))
+subplot(2,1,1)
+bar(x-0.5*0.35, q, width=0.35, alpha=0.3)
+xlim([0.5, 10.5])
+ylim([0., 1.05*max(hstack([q, p]))])
+gca().set_xticks(x)
+ylabel("Probability, $q(x)$")
+subplot(2,1,2)
 bar(x-0.5*0.35, p, width=0.35, alpha=0.3)
 xlabel("$x$", fontsize=20)
 ylabel("Probability, $p(x)$")
 xlim([0.5, 10.5])
+ylim([0., 1.05*max(hstack([q, p]))])
 gca().set_xticks(x)
-title("Posterior Distribution")
 savefig("distribution3.pdf", bbox_inches="tight")
 show()
 

### 2015-07-02 ms.tex
Nine possibilities instead of 10

@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.5]{distribution.pdf}
-\caption{A prior distribution $q(x)$, which we will use
-update to a posterior $p(x)$ given different kinds of testable information.
-\label{fig:distribution}}
-\end{center}
-\end{figure}
-
 The relative entropy of distribution $p$ from distribution $q$ is:
@@
 constraints of normalisation and any other constraints.
+
+Throughout this paper, we will look at examples of MaxEnt updating from a prior
+$q(x)$ to a posterior $p(x)$ in different situations where the available
+information takes different forms. The prior distribution for all of the
+examples is a discrete prior over nine possible values of $x$, and is shown
+in Figure~\ref{fig:distribution}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{distribution.pdf}
+\caption{A prior distribution $q(x)$, which we will use
+update to a posterior $p(x)$ given different kinds of testable information.
+\label{fig:distribution}}
+\end{center}
+\end{figure}
 
@@
 using the testable information $\left<(x - 5)^2\right>_p = 1$. The appropriate
-value of the lagrange multiplier is $\lambda=0.5163846$, and the posterior is
+value of the lagrange multiplier is $\lambda=0.516375$, and the posterior is
 shown in Figure~\ref{fig:distribution3}.

### 2015-07-02 plots.py

@@ -4,7 +4,7 @@ seed(123)
 rc("font", size=16, family="serif", serif="Computer Sans")
 rc("text", usetex=True)
 
-x = 1 + arange(0, 10)
+x = 1 + arange(0, 9)
 
 # Make a prior
 q = exp(0.5*randn(x.size))
@@ -16,7 +16,7 @@ q /= q.sum()
 bar(x-0.5*0.35, q, width=0.35, alpha=0.3)
 xlabel("$x$", fontsize=20)
 ylabel("Probability, $q(x)$")
-xlim([0.5, 10.5])
+xlim([0.5, 9.5])
 gca().set_xticks(x)
 title("Prior Distribution")
 savefig("distribution.pdf", bbox_inches="tight")
@@ -31,7 +31,7 @@ p /= p.sum()
 figure(figsize=(8, 10))
 subplot(2,1,1)
 bar(x-0.5*0.35, q, width=0.35, alpha=0.3)
-xlim([0.5, 10.5])
+xlim([0.5, 9.5])
 ylim([0., 1.05*max(hstack([q, p]))])
 gca().set_xticks(x)
 ylabel("Probability, $q(x)$")
@@ -39,24 +39,23 @@ subplot(2,1,2)
 bar(x-0.5*0.35, p, width=0.35, alpha=0.3)
 xlabel("$x$", fontsize=20)
 ylabel("Probability, $p(x)$")
-xlim([0.5, 10.5])
+xlim([0.5, 9.5])
 ylim([0., 1.05*max(hstack([q, p]))])
 gca().set_xticks(x)
 savefig("distribution2.pdf", bbox_inches="tight")
 show()
 
 # Another posterior
-lamb = 0.5163846 # The lagrange multiplier
+lamb = 0.516375 # The lagrange multiplier
 p = q.copy()
 p *= exp(-lamb*(x - 5.)**2)
 p /= p.sum()
 e = (p*(x - 5.)**2).sum()
-# print(e)
 
 figure(figsize=(8, 10))
 subplot(2,1,1)
 bar(x-0.5*0.35, q, width=0.35, alpha=0.3)
-xlim([0.5, 10.5])
+xlim([0.5, 9.5])
 ylim([0., 1.05*max(hstack([q, p]))])
 gca().set_xticks(x)
 ylabel("Probability, $q(x)$")
@@ -64,7 +63,7 @@ subplot(2,1,2)
[…]

### 2015-07-02 plots.py
The prior probabilities

@@ -10,6 +10,8 @@ x = 1 + arange(0, 9)
 q = exp(0.5*randn(x.size))
 q /= q.sum()
 
+print([round(qq, 3) for qq in q])
+
 # Probability of x \in {3, 4, 5} according to distribution q
 #print(sum(q[logical_and(x >= 3, x <= 5)]))
 

### 2015-07-02 ms.tex
The prior probabilities
Changed constraint (so it will be a row when hypothesis space is a 3x3 grid)

@@
 examples is a discrete prior over nine possible values of $x$, and is shown
-in Figure~\ref{fig:distribution}.
+in Figure~\ref{fig:distribution}. The nine prior probabilities are:
+
+\begin{eqnarray}
+\boldsymbol{q} = \{0.059, 0.167, 0.117, 0.048, 0.076, 0.231, 0.030, 0.082, 0.191\}.
+\end{eqnarray}
+
+The reason for choosing a ``ragged'' distribution is to avoid making any
+connection between MaxEnt and notions of smoothness or locality, since these
+do not actually play a role.
 
@@
 \begin{eqnarray}
-P(3 \leq x \leq 5) = 1.\label{eq:prob_one}
+P(7 \leq x \leq 9) = 1.\label{eq:prob_one}
 \end{eqnarray}
 Clearly, the distribution $q(x)$ doesn't satisfy this constraint. According
-to $q(x)$ the probability that $x$ is 3, 4, or 5 is 0.225, not 1.
+to $q(x)$ the probability that $x$ is 7, 8, or 9 is 0.303, not 1.
 Therefore, we
@@
 \left<
-\mathds{1}\left(3 \leq x \leq 5\right)
+\mathds{1}\left(7 \leq x \leq 9\right)
 \right>_p = 1.

### 2015-07-02 plots.py

@@ -11,6 +11,7 @@ q = exp(0.5*randn(x.size))
 q /= q.sum()
 
 print([round(qq, 3) for qq in q])
+print(q[x >= 7].sum())
 
 # Probability of x \in {3, 4, 5} according to distribution q
 #print(sum(q[logical_and(x >= 3, x <= 5)]))
@@ -27,7 +28,7 @@ show()
 
 # Make a posterior
 p = q.copy()
-p[logical_or(x < 3, x > 5)] = 0.
+p[logical_or(x < 7, x > 9)] = 0.
 p /= p.sum()
 
 figure(figsize=(8, 10))

### 2015-07-03 ms.tex
grid
Tables
Grid has meaning

@@
 \usepackage[utf8]{inputenc}
+\usepackage{color, colortbl}
 
+\definecolor{Gray}{gray}{0.5}
 \renewcommand{\topfraction}{0.85}
@@
 
+The prior probabilities can also be laid out in a grid:
+
+\begin{center}
+\begin{tabular}{|ccc|}
+\hline
+0.059 & 0.167 & 0.117\\
+0.048 & 0.076 & 0.231\\
+0.030 & 0.082 & 0.191\\
+\hline
+\end{tabular}
+\end{center}
+
+Updating using MaxEnt, using the same constraint as before, is equivalent
+to ruling out the first two rows of this grid and maintaining the third.
+\begin{center}
+\begin{tabular}{|ccc|}
+\hline
+\rowcolor{Gray}
+0.059 & 0.167 & 0.117\\
+\rowcolor{Gray}
+0.048 & 0.076 & 0.231\\
+0.030 & 0.082 & 0.191\\
+\hline
+\end{tabular}
+$\Longrightarrow$
+\begin{tabular}{|ccc|}
+\hline
+0.000 & 0.000 & 0.000\\
+0.000 & 0.000 & 0.000\\
+0.099 & 0.270 & 0.630\\
+\hline
+\end{tabular}
+\end{center}
+
+In Bayesian inference, we usually want to infer the value of a parameter
+$\theta$ from the value of a datum $D$. Suppose there are three possible
+$\theta$ values ($\theta_1$, $\theta_2$, and $\theta_3$) and three possible
+$D$ values ($D_1$, $D_2$, and $D_3$). Then the hypothesis space
+consists of nine propositions, created using logical {\bf and}; these
+propositions are all of the form
+$(\theta = \theta_i) \wedge (D = D_j)$ where $i, j \in \{1, 2, 3\}$.
+
 \subsection{Skilling's criticism}

### 2015-07-28 ms.tex
New sections
Working on the intro

@@
 \section{Introduction}
-The principle of maximum entropy (MaxEnt) is an idea in probability theory
-that is usually associated with \citet{jaynes}, although it has appeared in
+It is now well established that degrees of certainty can and should be modelled
+with probability theory. The resulting framework is usually called Bayesian
+inference, whose key feature is the updating of probabilities to incorporate
+new information when it is learned.
+
+The principle of maximum entropy (MaxEnt) is an idea that was developed...
+
+It is usually associated with \citet{jaynes}, although it has appeared in
 various guises in the work of others \citep[e.g.][]{gibbs, boltzmann, shannon}.
 
-The principle may be used
-to {\it assign} or {\it update} a
+MaxEnt can be used either to {\it assign} or to {\it update} a
 subjective\footnote{in the sense that the probability distribution is a model
@@
 
-The principle is very intuitively compelling
-and there are some axiomatic arguments in its favour
-\citep[e.g.][]{shore_johnson, 2006AIPC..872...31C, 2010arXiv1008.4831K}
-and counterexamples to alternatives \citep[e.g.][]{presse}.
-However, MaxEnt has also been widely
+There are some axiomatic arguments supporting MaxEnt
+\citep[e.g.][]{shore_johnson, 2006AIPC..872...31C, 2010arXiv1008.4831K},
+as well as counterexamples to possible alternatives \citep[e.g.][]{presse}.
+However, there is no consensus among Bayesians of the status of MaxEnt: is
+it a valid and potentially useful fundamental principle, some kind of an
+approximation or computational trick, or a dead end that is solely of
+historical interest?
+
+has also been widely
 misapplied (even by some of its staunchest defenders), misunderstood,
@@
 
-\section{MaxEnt with constraints on marginals: ``hierarchical Bayes''}
+\section{MaxEnt with constraints on marginals}
+\subsection{Heirarchical Bayes}
 Suppose we have a discrete prior distribution $q(\xx)$. Consider some
@@
 \end{eqnarray}
+
+\subsection{Jeffrey Conditionalisation}
 

### 2015-07-28 ms.tex
Sentences

@@
 
+There are several possible reasons for the lack of consensus.
+
 has also been widely
@@
 Consequently, most modern Bayesians pay little attention to the principle,
-although there is a tendency among physicists to invoke it as a justification
+although there is a tendency among physicists, raised on \citet{jaynes},
+to invoke it as a justification
 for a prior distribution (be it uniform, exponential, gaussian, or whatever).

### 2015-08-10 ms.tex
Mentioned MaxEnt-as-regulariser

@@
 as well as counterexamples to possible alternatives \citep[e.g.][]{presse}.
-However, there is no consensus among Bayesians of the status of MaxEnt: is
+However, there is no consensus among Bayesians about the status of MaxEnt. Is
 it a valid and potentially useful fundamental principle, some kind of an
-approximation or computational trick, or a dead end that is solely of
+approximation or computational trick, or a dead end that is only of
 historical interest?
@@
 There are several possible reasons for the lack of consensus. 
+One is that the name ``MaxEnt'' has been used to refer not just to the principle
+for updating probability distributions, but also to a specific choice of
+regularisation term in optimisation-based methods for inverse problems
+\citep{}, among other things. Since Bayesian inference is
+a more principled way to deal with the uncertainty than regularised
+optimisation, this leads to the idea that Bayesian inference
+{\it supersedes} MaxEnt, and therefore that MaxEnt can be ignored.
 
-has also been widely
-misapplied (even by some of its staunchest defenders), misunderstood,
-and poorly defended (at times, even by Jaynes himself).
+In addition, many defences and explanations of MaxEnt in the literature
+are weak.
+
 Consequently, most modern Bayesians pay little attention to the principle,

### 2015-08-10 ms.tex
Fixed wording

@@
 a more principled way to deal with the uncertainty than regularised
-optimisation, this leads to the idea that Bayesian inference
-{\it supersedes} MaxEnt, and therefore that MaxEnt can be ignored.
-
+optimisation, MaxEnt seems obsolete --- although it is obvious that
+an argument against one idea does not imply much about another idea that
+happens to share the same name.
 In addition, many defences and explanations of MaxEnt in the literature

### 2015-08-10 ms.tex
Get rid of capital As

@@
 We start with a {\it hypothesis space} of mutually exclusive and
-exhaustive propositions $A_1$, $A_2$, ..., $A_N$ which we will usually
+exhaustive propositions which we can (without loss of generality)
 think of as possible values of an unknown quantity $x$. For example,
-$A_1 \equiv $``$x=1$'', $A_2 \equiv $``$x=2$'', and so on.
+the propositions might be ``$x=1$'', ``$x=2$'', and so on.
 On the basis of background
@@
 uncertainty by probability distributions over the hypothesis space,
-such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
+such as $\{p_i\}_{i=1}^N$ where $P(x=x_i) = p_i$.
 In the standard loose Bayesian notation we write this distribution simply
-as $p(x)$.
+as $p(x)$, the probability distribution for $x$.
 
@@
 using the sum and product rules. For example, the probability of
-($A_4$ {\bf or} $A_5$) is $p_4 + p_5$, and the probability of $A_5$ given
-($A_5$ {\bf or} $A_8$) is $p_5/(p_5 + p_8)$. The rules of probability must
+($x=4$ {\bf or} $x=5$) is $p_4 + p_5$, and the probability of $x=5$ given
+($x=5$ {\bf or} $x=8$) is $p_5/(p_5 + p_8)$. The rules of probability must
 be obeyed if the rules for combining are to remain consistent

### 2015-08-10 ms.tex
A bit of tidying

@@
 
-Of course, $p(x)$ must be non-negative and sum to 1.
+Of course, $p(x)$ must be non-negative and sum to 1 in order to be a valid
+probability distribution.
 From this probability distribution, various probabilities can be derived
@@
 and only if $p$ happens to be the same as $q$.
-However, it is not symmetric and does not satisfy
+However, $H$ is not symmetric and does not satisfy
 other properties of a distance.
-and we are to choose the distribution $p$ to maximise $H$ subject to the
-constraints of normalisation and any other constraints.
 
@@
 {\it a constraint that our probability distribution should satisfy}. This is
+the kind of information MaxEnt uses, and is
 different from the kind of information we normally use in Bayesian inference,
@@
 
-The posterior $p$ will satisfy the constraint given in the testable information,
-and will be as close to $q$ as possible while doing so.
+The posterior $p$ must satisfy the constraint given in the testable information,
+and should be as close to $q$ as possible while doing so. The criterion for
+``closeness'' is the relative entropy $H(p; q)$:
+we should choose the distribution $p$ to maximise $H$ subject to the
+constraints of normalisation (i.e. $\sum_i q_i = 1$)
+and the testable information.
 

### 2015-08-10 ms.tex
COmpleted sentence

@@
 The reason for choosing a ``ragged'' distribution is to avoid making any
-connection between MaxEnt and notions of smoothness or locality, since these
-do not actually play a role.
+suggestion that MaxEnt relates to the ``smoothness'' of a distribution. The
+entropy formula has no notion of certain hypotheses being neighbours of others.
+I also chose the non-uniform prior to emphasise the role of MaxEnt as
+a tool for updating probabilities, rather than assigning prior probabilities.
 
